---
title: "Robust Estimation of Beer Production Data using Bootstrap Resampling"
author: "Gaurav Sharma"
date: "24/06/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---
# Prerequisites
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
library(tidyverse)
library(tidymodels)
```

# Lets load the data

```{r}
brewing_materials_raw <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-31/brewing_materials.csv")
brewing_materials_raw
```

# Lets explore the data a bit to understand
```{r}
brewing_materials_raw %>% group_by(type) %>% summarise(n = sum(month_current)) %>% arrange(desc(n))
brewing_materials_raw %>% count(type, wt = month_current,sort = T) # Shorter way of doing the same thing

```

# More Exploration
```{r}
brewing_filtered <- brewing_materials_raw %>%
    filter(
        type %in% c("Malt and malt products",
                    "Sugar and syrups",
                    "Hops (dry)"),
        year < 2016,
        month != 12
    ) %>%
    mutate(date = lubridate::ymd(paste(year, "-", month, "-01")))

brewing_filtered %>%
    ggplot(aes(x = date, y = month_current, color = type)) +
    geom_point(size = 2)

brewing_materials <- brewing_filtered %>% 
    select(date, type, month_current) %>% 
    pivot_wider(names_from = type,
                values_from = month_current) %>% 
    janitor::clean_names()

brewing_materials %>% 
    ggplot(aes(malt_and_malt_products, sugar_and_syrups)) +
    geom_point() +
    geom_smooth(method = 'lm') +
    theme_light()
```

# Lets fit a simpler linear model assuming that if there is no malt then there will be no requirement of sugar

```{r}
beer_fit <- lm(sugar_and_syrups ~ 0 + malt_and_malt_products, data = brewing_materials)

summary(beer_fit)
tidy(beer_fit)
```

# Lets create a bootstrap sample

```{r}
set.seed(123)
beer_boot <- bootstraps(data = brewing_materials,
                        times = 1e3,
                        apparent = TRUE)
```

# Lets map some functions and check results
```{r}
beer_models <-
    beer_boot %>%
    mutate(model = map(
        splits,
        ~ lm(sugar_and_syrups ~ 0 + malt_and_malt_products,
             data = .)
    ))

beer_coefs <- beer_models %>% 
    mutate(coef_info = map(model, tidy)) %>% 
    unnest(coef_info)
```

# Lets evaluatet the results

```{r}
beer_coefs %>%
    ggplot(aes(estimate)) +
    geom_histogram() +
    geom_vline(
        xintercept = mean(beer_coefs$estimate),
        color = 'tomato',
        size = 2
    ) +
    annotate(
        geom = "text",
        x = 0.2155,
        y = 77,
        label = "Mean of resampled estimates",
        size = 5,
        color = 'tomato'
    ) +
    annotate(
        geom = "curve",
        x = 0.208,
        xend = 0.212,
        y = 80,
        yend = 77,
        curvature = -0.3,
        size = 1,
        color = 'tomato'
    )
```

# Lets see another summary for these models
```{r}
beer_models %>% 
    mutate(glance = map(model, glance)) %>% 
    unnest(glance)
```

# Lets check the fitted values
```{r}
beer_models %>% 
    sample_n(200) %>% 
    mutate(augment = map(model, augment)) %>% 
    unnest(augment) %>% 
    ggplot(aes(malt_and_malt_products, sugar_and_syrups)) +
        geom_point(show.legend = F) +
    geom_line(aes(y = .fitted, group = id, color = 'pink', alpha = 0.1),
              show.legend = F)
    
```

# Thats how we can use tidymodels workflow to see how predictions can be seen visually using resampled data (Bootstrapped)





















